Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-06 eswc-2012/phdsymp.tex
advices in abstract
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@159 43ef1190-90fd-4dd7-a769-d0121f02b80e

  Discontent with current state of the art in benchmarking prompts the
  author to focus on the evaluation problem and to challenge the
  notion that a ``one-size-fits-all'' benchmark is impossible.
\end{abstract}

>>>>

  Discontent with current state of the art in benchmarking prompts the
  author to focus on the evaluation problem and to investigate whether
  we can provide better advices to new users selecting a SPARQL engine
  to use.
\end{abstract}
